Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-08-05 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Work more on draft.

@@

```{r echo = FALSE, message = FALSE, warning = FALSE}
all_distance <- county_distance(counties = my_fips, start_year = 1988, 
                        end_year = 2011, dist_limit =100)

distance_exposed %>%
        mutate(storm_id = gsub("-", " (", storm_id),
               storm_id = paste0(storm_id, ")")) %>%
        kable(col.names = c("Storm", "# of exposed counties"),
              caption = "Top 10 storms based on the number of counties exposed, using a metric of distance.")
```

Here are plots of the top four storms based on number of counties exposed by distance:

```{r echo = FALSE, fig.width = 10, fig.height = 8}
top_distance_exposed <- function(storm_id){
        my_map <- map_distance_exposure(storm_id, dist_limit = 100)
        my_map <- map_tracks(storm = storm_id, plot_object = my_map, 
                             plot_points = FALSE) + 
                ggtitle(paste0(gsub("-", " (", storm_id), ")"))
}

@@

```{r echo = FALSE, message = FALSE, warning = FALSE}
all_rain <- county_rain(counties = my_fips, start_year = 1988, 
                        end_year = 2011, rain_limit = 75, dist_limit = 500,
                        days_included = -1:1)

rain_exposed %>%
        mutate(storm_id = gsub("-", " (", storm_id),
               storm_id = paste0(storm_id, ")")) %>%
        kable(col.names = c("Storm", "# of exposed counties"),
              caption = "Top 10 storms based on the number of counties exposed, using a metric of rainfall.")
```

Here are plots of the exposed counties for the top 4 storms based on that rain metric:

```{r echo = FALSE, fig.width = 10, fig.height = 8}
top_rain_exposed <- function(storm_id){
        my_map <- map_rain_exposure(storm_id, rain_limit = 75, 
                                    dist_limit = 500)
        my_map <- map_tracks(storm = storm_id, plot_object = my_map, 
                             plot_points = FALSE) + 
                ggtitle(paste0(gsub("-", " (", storm_id), ")"))
}

@@

```{r echo = FALSE, message = FALSE, warning = FALSE}
all_wind <- county_wind(counties = my_fips, start_year = 1988, 
                        end_year = 2011, wind_limit = 15)

wind_exposed %>%
        mutate(storm_id = gsub("-", " (", storm_id),
               storm_id = paste0(storm_id, ")")) %>%
        kable(col.names = c("Storm", "# of exposed counties"),
              caption = "Top 10 storms based on the number of counties exposed, using a metric of wind.")
```

Here are plots of the top four storms based on number of counties exposed by wind:

```{r echo = FALSE, fig.width = 10, fig.height = 8}
top_wind_exposed <- function(storm_id){
        my_map <- map_wind_exposure(storm_id, wind_limit = 18)
        my_map <- map_tracks(storm = storm_id, plot_object = my_map, 
                             plot_points = FALSE) + 
                ggtitle(paste0(gsub("-", " (", storm_id), ")"))
}

>>>>

We created plots of the top four storms, in terms of the number of counties classified as exposed, for exposure metrics of distance (Figure \ref{fig:top_four_distance}), rain (Figure \ref{fig:top_four_rain}), wind (Figure \ref{fig:top_four_wind}), flood events (Figure \ref{fig:top_four_flood}), and tornado events (Figure \ref{fig:top_four_tornado}).

```{r top_four_distance, echo = FALSE, fig.width = 10, fig.height = 8, fig.align = "center", fig.cap = "Counties exposed for the top four storms over the study period, in terms of distance-based exposure."}
top_distance_exposed <- function(storm_id){
        my_map <- map_distance_exposure(storm_id, dist_limit = 100)
        my_map <- map_tracks(storm = storm_id, plot_object = my_map, 
                             plot_points = FALSE) + 
                ggtitle(paste0(gsub("-", " (", storm_id), ")"))
}

all_distance <- county_distance(counties = my_fips, start_year = 1988, 
                        end_year = 2011, dist_limit =100)

```{r top_four_rain, echo = FALSE, fig.width = 10, fig.height = 8, fig.align = "center", fig.cap = "Counties exposed for the top four storms over the study period, in terms of distance-based exposure."}
top_rain_exposed <- function(storm_id){
        my_map <- map_rain_exposure(storm_id, rain_limit = 75, 
                                    dist_limit = 500)
        my_map <- map_tracks(storm = storm_id, plot_object = my_map, 
                             plot_points = FALSE) + 
                ggtitle(paste0(gsub("-", " (", storm_id), ")"))
}

all_rain <- county_rain(counties = my_fips, start_year = 1988, 
                        end_year = 2011, rain_limit = 75, dist_limit = 500,
                        days_included = -1:1)

```{r top_four_wind, echo = FALSE, fig.width = 10, fig.height = 8, fig.align = "center", fig.cap = "Counties exposed for the top four storms over the study period, in terms of distance-based exposure."}
top_wind_exposed <- function(storm_id){
        my_map <- map_wind_exposure(storm_id, wind_limit = 15)
        my_map <- map_tracks(storm = storm_id, plot_object = my_map, 
                             plot_points = FALSE) + 
                ggtitle(paste0(gsub("-", " (", storm_id), ")"))
}

all_wind <- county_wind(counties = my_fips, start_year = 1988, 
                        end_year = 2011, wind_limit = 15)

```{r top_four_flood, echo = FALSE, fig.width = 10, fig.height = 8, fig.align = "center", fig.cap = "Counties exposed for the top four storms over the study period, in terms of flood event-based exposure."}
top_flood_exposed <- function(storm_id){
        my_map <- map_event_exposure(storm_id, event_type = "flood")
        my_map <- map_tracks(storm = storm_id, plot_object = my_map, 
                             plot_points = FALSE) + 
                ggtitle(paste0(gsub("-", " (", storm_id), ")"))
}

all_flood <- county_events(counties = my_fips, start_year = 1996, 
                        end_year = 2011, event_type = "flood")

flood_exposed <- all_flood %>%
        group_by(storm_id) %>%
        summarize(number_of_counties_exposed = n()) %>%
        arrange(desc(number_of_counties_exposed)) %>%
        top_n(10) %>%
        ungroup() %>%
        mutate(storm_id = as.character(storm_id))

n <- 4
flood_plots <- lapply(flood_exposed$storm_id[1:n], top_flood_exposed)
names(flood_plots) <- letters[1:n]
grid.arrange(flood_plots$a, flood_plots$b, flood_plots$c,
             flood_plots$d, ncol = 2)
```

```{r top_four_tornado, echo = FALSE, fig.width = 10, fig.height = 8, fig.align = "center", fig.cap = "Counties exposed for the top four storms over the study period, in terms of tornado event-based exposure."}
top_tornado_exposed <- function(storm_id){
        my_map <- map_event_exposure(storm_id, event_type = "tornado")
        my_map <- map_tracks(storm = storm_id, plot_object = my_map, 
                             plot_points = FALSE) + 
                ggtitle(paste0(gsub("-", " (", storm_id), ")"))
}

all_tornado <- county_events(counties = my_fips, start_year = 1996, 
                        end_year = 2011, event_type = "tornado")

tornado_exposed <- all_tornado %>%
        group_by(storm_id) %>%
        summarize(number_of_counties_exposed = n()) %>%
        arrange(desc(number_of_counties_exposed)) %>%
        top_n(10) %>%
        ungroup() %>%
        mutate(storm_id = as.character(storm_id))

n <- 4
tornado_plots <- lapply(tornado_exposed$storm_id[1:n], top_tornado_exposed)
names(tornado_plots) <- letters[1:n]
grid.arrange(tornado_plots$a, tornado_plots$b, tornado_plots$c,
             tornado_plots$d, ncol = 2)
```

@@

```{r echo = FALSE}
distance_exposed %>%
        mutate(storm_id = gsub("-", " (", storm_id),
               storm_id = paste0(storm_id, ")")) %>%
        kable(col.names = c("Storm", "# of exposed counties"),
              caption = "Top 10 storms based on the number of counties exposed, using a metric of distance.")
```

@@

```{r echo = FALSE}
rain_exposed %>%
        mutate(storm_id = gsub("-", " (", storm_id),
               storm_id = paste0(storm_id, ")")) %>%
        kable(col.names = c("Storm", "# of exposed counties"),
              caption = "Top 10 storms based on the number of counties exposed, using a metric of rainfall.")
```

@@

```{r echo = FALSE}
wind_exposed %>%
        mutate(storm_id = gsub("-", " (", storm_id),
               storm_id = paste0(storm_id, ")")) %>%
        kable(col.names = c("Storm", "# of exposed counties"),
              caption = "Top 10 storms based on the number of counties exposed, using a metric of wind.")
```
